---
title: "Week 4 Synchronous"
author: "Kyle Walter"
date: "2/3/2021"
output: word_document
---

let's load the data
```{r}
require(PerformanceAnalytics)
```

Display the data
```{r}
tail(disney.monthly)
tail(no.risk)
```


Compute the excess returns on DIS and the S&P 500 Index in excess of 3-month Treasury Bills
```{r}
disney.excess.monthly <- disney.monthly-no.risk
market.excess.monthly <- market.monthly-no.risk
```

Excess Return = Past Return minus Past Risk Free Return

Next let's plot Disney's Market vs the Market
```{r}
chart.Regression(disney.excess.monthly, market.excess.monthly, fit = F, main = "My Lame (noninteractive) Chart", xlab = "US Market", ylab = "Disney Stock")
```
Let's find the linerar realtionship
```{r}
mickey<- lm(disney.excess.monthly~market.excess.monthly)
chart.Regression(disney.excess.monthly, market.excess.monthly, fit = F)
abline(mickey)
```
Equation is called a linear model because the line doesn't pass through the actual points perfectly. The fit is a line which is why it is recognized as Linear Model.

To see the value of the coefficent, just type the name of the saved model
```{r}
mickey
```

Company specific risk or firmwide risk, specific to a company and news about the company.

Market specific risk, are the market adjustments. If something affects overall market it cannot be avoided. The Beta Coefficent predicts what happens to the stock in a market movement. So Disney in this case will move relative to the market.