---
title: "Week 4 Async"
author: "Kyle Walter"
date: "1/30/2021"
output: word_document
---

Use R and download teh index data for S&P500 and price data for Apple, INC stocks. Download the data between the first trading day of May 2015 and the last trading day of April 2020.

Load the Packages needed for this exercise
```{r}
require(quantmod)
require(PerformanceAnalytics)
```

```{r}
getSymbols(c("AAPL","^GSPC"), from="2015-05-01", to="2020-05-01")
```

Inspect the Data
```{r}
head(GSPC)
head(AAPL)
```

Computing the monthly returns
```{r}
monthlyReturn(AAPL[,6])->apple.monthly
monthlyReturn(GSPC[,6])->market.monthly
```

Inspect the data
```{r}
head(market.monthly)
head(apple.monthly)
```

Next get the treasury bills
```{r}
getSymbols("DGS3MO", src="FRED") #Treasury Data will came with all time
head(DGS3MO)
no.risk <- DGS3MO[,1]/1200
head(no.risk)
tail(no.risk)
```

Next we'll calculate the excess return
```{r}
apple.excess.monthly <- apple.monthly-no.risk
head(apple.excess.monthly)
```

Next lets create the market comparison
```{r}
market.excess.monthly <- market.monthly-no.risk
```

Next let's plot Apple vs the Market excess return
```{r}
chart.Regression(apple.excess.monthly, market.excess.monthly, fit=F)
```
Next let put this into a linear model
```{r}
cider <- lm(apple.excess.monthly~market.excess.monthly)
chart.Regression(apple.excess.monthly, market.excess.monthly, fit=F)
abline(cider)
cider
```

Now that we'veworked through a problem in class let's practice on our own.
The problem, predict the beta coefficent for JetBlue Airways Corp.

```{r}
getSymbols("JBLU", from ="2015-05-01", to="2020-05-01")
skies <- monthlyReturn(JBLU[,6])
skies.excess.monthly <- skies-no.risk
lm(skies.excess.monthly~market.excess.monthly)
```







